### 2023-01-27 paper-thesis/chapters/22-adding-datatypes.tex
Work from yesterday
Minor writing changes

A difference between Agda and our implementation is that Agda has case matching as a native construct, whereas we chose to use eliminators \todo{Citation}. An eliminator is a function that can be used to case match on a data type. For example, the eliminator of the \verb|Nat| type above is:
\begin{lstlisting}
elim Nat : P: (v: Nat -> Type) -> P Z 
	-> (x: Nat -> P x -> P (S x)) -> n: Nat -> P n
\end{lstlisting}

@@

	\item Type-check the rest of the program with scope \verb|s4|.
\end{enumerate}
For example, for the following inductive datatype:
\begin{lstlisting}
data Eq (T : Type) : (e1 : T) (e2 : T) -> Type where
	refl : e : T -> Eq e e;
...
\end{lstlisting}
Figure \ref{scope-graph-eq} shows the scope graph generated by this data type.
\begin{figure}[!h]
	\begin{framed}
		\centering
		\begin{tikzpicture}[scopegraph, node distance = 6.5em and 5em]
			% S0 and S1 node
			\node[scope] (s0) {$s0$};
			\node[scope, below = 2em of s0] (s1) {$s1$};
			\draw (s1) edge[lbl={P}] (s0);

>>>>

A difference between Agda and our implementation is that Agda has case matching as a native construct, whereas we chose to use eliminators~\cite{eliminators}. An eliminator is a function that can be used to case match on a data type. For example, the eliminator of the \verb|Nat| type above is:
\begin{lstlisting}
elim Nat : P: (v: Nat -> Type) -> P Z 
	-> (x: Nat -> P x -> P (S x)) -> n: Nat -> P n
\end{lstlisting}

@@

	\item Type-check the rest of the program with scope \verb|s4|.
\end{enumerate}
For example, for the following inductive datatype:
\begin{lstlisting}
data Eq (T : Type) : (e1 : T) (e2 : T) -> Type where
	refl : e : T -> Eq e e;
...
\end{lstlisting}
Figure \ref{scope-graph-eq} shows the scope graph generated by this data type.
\begin{figure}[!ht]
	\begin{framed}
		\centering
		\begin{tikzpicture}[scopegraph, node distance = 6.5em and 5em]
			% S0 and S1 node
			\node[scope] (s0) {$s0$};
			\node[scope, below = 2em of s0] (s1) {$s1$};
			\draw (s1) edge[lbl={P}] (s0);
